```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,error=FALSE}
 library(ChemmineOB) 
 library(knitcitations)
```

ChemmineOB
==========

Kevin Horan & Thomas Girke

`r format(Sys.time(),"%B %d, %Y")`

Introduction
-----------

*ChemmineOB* provides an R interface to a subset of
cheminformatics functionalities implemented by the OpelBabel C++ project
`r citep(c("10.1186/1752-153X-2-5", "10.1186/1758-2946-3-33"))`. OpenBabel is an open source
cheminformatics toolbox that includes utilities for structure format
interconversions, descriptor calculations, compound similarity searching
and more. *ChemineOB* aims to make a subset of these
utilities available from within R. For non-developers,
*ChemineOB* is primarily intended to be used from
*ChemmineR* `r citep(c("10.1093/bioinformatics/btn307", "10.1093/nar/gkr320","10.1093/bioinformatics/btt475"))`
as an add-on package rather than used directly.

Installation
-----------

To use the *ChemmineOB* package on Linux or Mac, OpenBabel
2.3.0 or greater needs to be installed on a system. On Linux systems,
the OpenBabel header files are also required in order to compile *ChemmineOB*. The windows distribution
will include its own version of OpenBabel. The OpenBabel site
(<http://openbabel.org/wiki/Get_Open_Babel>) provides excellent
instructions for installing the OpenBabel software on Mac or Linux
systems. The *ChemmineR* and *ChemmineOB*
packages can be installed from within R with the
`biocLite` install script.

```{r eval=FALSE, tidy=FALSE}
source(“http://bioconductor.org/biocLite.R”) 
biocLite(c(“ChemmineR”, “ChemmineOB”)) 
library(“ChemmineR”) 
library(“ChemmineOB”) 
```


If the installation fails on Linux, you may need to manually set the
locations of the open babel libraries and header files. This is best
done through configure flags. For example, at the command prompt do:

```Bash
$ R CMD INSTALL –configure-args=’–with-openbabel-include=...  –with-openbabel-lib=...’ <ChemmineOB package file>
```

where the ’…’ are replaced by the relevant paths. See the README file
for more details.
User Manual in ChemmineR Vignette
-----------

Detailed instructions for using *ChemmineOB* are provided
in the vignette of the *ChemmineR* package instead of this
document. The main reason for consolidating the documentation in one
central document rather than distributing it across several vignettes is
that it helps minimizing duplications and inconsistencies. It also is
the more suitable format for providing a task-oriented description of
functionalities for users. To obtain an overview of the OpenBabel
utilities supported by *ChemmineOB*, we recommend
consulting the *OpenBabel Functions* section of the
*ChemmineR* vignette. To open the *ChemmineR*
vignette from R, one can use the following command.

```{r eval=FALSE, tidy=FALSE}
 vignette(“ChemmineR”) 
```

Version Information
-----------

```{r sessionInfo, results='asis'}
 sessionInfo()
```

Funding
-----------

This software was developed with funding from the National Science
Foundation:
[ABI-0957099](http://www.nsf.gov/awardsearch/showAward.do?AwardNumber=0957099),
2010-0520325 and IGERT-0504249.

References
-----------
```{r biblio, echo=FALSE, results='asis'}
   bibliography()
```
